
\documentclass[11pt,letterpaper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{multicol}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[hyperref]{}
\usepackage[scale=0.9]{geometry} 
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Aman} % Your first name
\familyname{Roy} % Your last name

\address {Pune, Maharashtra, India}{\href{http://github.com/aman-roy}{github.com/aman-roy}} \title{Computer Science Undergrad}
\homepage{amanroy.me}{amanroy.me}
\mobile{(+91) 7050708296, 8208455699}
\email {royaman8757@gmail.com}
\begin{document}

\makecvtitle % Print the CV title

%-----------------------------------------------------
%	PROJECTS SECTION
%-----------------------------------------------------
\section{Projects}

\cventry{AUG 2019--Ongoing}{NOTAS}{\textit{A Notes sharing platform}}{}{}{\begin{itemize}
\item A web application implemented in Django 2.x to make notes sharing hassle free.
\item Front-end is made using HTML/CSS/JS and  Materializecss framework.
\end{itemize}
\hspace{0.39cm}Project link - \href{https://github.com/aman-roy/Notas}{github.com/aman-roy/Notas}}

\cventry{JUN--JUL 2019}{EXSC}{\textit{Extended Substitution Cipher}}{}{}{\begin{itemize}
\item Implementation of a new kind of cipher based on substitution cipher. It uses PRNG for generating deterministic multiple tables for encryption.
\item Packaged it using PyPI and can be installed using pip.
\end{itemize}
\hspace{0.39cm}Project link - \href{https://github.com/aman-roy/Extended-Substitution-Cipher}{github.com/aman-roy/Extended-Substitution-Cipher}}

\cventry{MAR 2019}{Automatic Active Server Communication Alerts}{\textit{Hackathon Project}}{}{}{\begin{itemize}
\item Flask and celery based responsive web application for checking the network breakdowns of multiple websites in a simplified way.
\item In case of receiving the critical status codes from the website or the server crash, the acknowledgements will be send using SMS API to the maintainer of the website. 
\end{itemize}
\hspace{0.39cm}Project link - \href{https://github.com/Code-Blooded-007/Backend}{github.com/Code-Blooded-007/Backend}}

\cventry{JAN--MAR 2019}{Movie Booking Management System}{\textit{OOPS Lab Project}}{}{}{\begin{itemize}
\item Project is implemented in C++ and can be used for managing all the movie booking related data. 
\item Terminal based application with a very user friendly environment.
\end{itemize}}

\cventry{JUL--SEP 2018}{BloodBank}{\textit{DS Lab Project}}{}{}{\begin{itemize}
\item BloodBank management system developed in C language to do book keeping and data manipulation.
\item Most of the core data structures are implemented in a very optimal way.
\end{itemize}
\hspace{0.39cm}Project link - \href{https://github.com/aman-roy/BloodBank}{github.com/aman-roy/BloodBank}}

\cventry{FEB--MAR 2018}{Auto FB Confess}{\textit{Personal Project}}{}{}{\begin{itemize}
\item A simple flask based app which helps in posting to Facebook pages automatically. 
\item It can be used to post directly to Facebook pages without any use of middle man with the help of FB SDK API.
\end{itemize}
\hspace{0.39cm}Project link - \href{https://github.com/aman-roy/Auto-FB-Confess}{github.com/aman-roy/Auto-FB-Confess}}

\cventry{MAY--OCT 2017}{Stalkhub}{\textit{Personal Project}}{}{}{\begin{itemize}
\item StalkHub is a flask-based web app which uses GitHub api v3 to retrieve users data and renders it beautifully.
\end{itemize}
\hspace{0.39cm}Project link - \href{https://github.com/aman-roy/StalkHub}{github.com/aman-roy/StalkHub}
\hspace{0.39cm}Working live - \href{http://stalkhub.amanroy.me/}{stalkhub.amanroy.me}}

\cventry{Feb 2016}{mp3\_Downloader}{\textit{Personal Project}}{}{}{\begin{itemize}
\item A simple python script from which you can download the songs by just entering the name.
\item You can also download by entering a list of name, YouTube link or list of YouTube links.
\end{itemize}
\hspace{0.39cm}Project link - \href{https://github.com/aman-roy/mp3_downloader}{github.com/aman-roy/mp3\_downloader}}

%-----------------------------------------------------
%	EDUCATION SECTION
%-----------------------------------------------------
\section{Education}

\cventry{2017--Present}{G.H. Raisoni College of Engineering and Management, Pune}{}{}{}{Computer Engineering Bachelors of Technology, CGPA -- \textbf{9.22/10} \newline Expected Graduation Year - 2021}  




%----------------------------------------------------------------------------------------
%	Publication
%----------------------------------------------------------------------------------------

\section{Publication}

\cventry{SEPT 2019}{R. Aman et. al., "Advancement on Substitution Cipher using Multiple Substitution Table" 2019 5th (ICCUBEA), Pune, India, \textcopyright    IEEE}{}{}{}{Accepted for publication}


%----------------------------------------------------------------------------------------
%	Achievements SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}

\cventry{2019}{}{}{}{}{\textbf{Ranked 7\textsuperscript{th}} in Python developer section and \textbf{3\textsuperscript{rd}} in HTML ranking on \href{http://git-awards.com/users/aman-roy}{GitHub} in Pune, India}
\cventry{2019}{}{}{}{}{Runner up in "\textbf{Smart India Hackathon} - Software edition" among \textbf{2 lacks+} participants.}
\cventry{2019}{}{}{}{}{Got \textbf{1\textsuperscript{st} prize} in College level programming competition "Codebuzz".}
\cventry{2018}{}{}{}{}{Got \textbf{2\textsuperscript{nd} prize} in mini modeling competition organized for first year students.}
\cventry{2018}{}{}{}{}{\textbf{Semi finalist} in blackout coding organized by MIT-ADT University.}
\cventry{2018}{}{}{}{}{Got \textbf{1\textsuperscript{st} prize} in research paper presentation in National level competition TRPCS and won cash prizes.}
\cventry{2018}{}{}{}{}{Reported a security flaw in \textbf{Amazon India website} that enables user to opt for pay on delivery option even when it is not available in that area.}
\cventry{2013}{}{}{}{}{Got Qualified for \textbf{NMCMSE Scholarship} and received financial help for \textbf{4 years} from state government.}


%-----------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------

\section{Technical Skills}

\cvitem{Languages}{C, C++, Python, PHP, Shell script}
\cvitem{Frameworks}{Django, Flask}
\cvitem{Front-end}{HTML/CSS/JS, Bootstrap, Materializecss}
\cvitem{Databases}{MySQL, SQLite}
\cvitem{Core}{DS and Algorithms, Cryptography}
\cvitem{VCS}{Git, GitHub, Bitbucket}



%-----------------------------------------------------
%	Additional Training SECTION
%-----------------------------------------------------

\section{Additional Training}

\cventry{JUN 2018--NOV 2018}{Introduction to Computer Science and Programming Using Python
}{edx.org}{}{}{MITx: 6.00.1x \newline  This course is the first of a two-course sequence: Introduction to Computer Science and Programming Using Python, and Introduction to Computational Thinking and Data Science. \newline Completed with \textbf{95/100} marks. Certificate - \href{http://tiny.cc/amanmitx}{tiny.cc/amanmitx}}

\cventry{AUG 2016--MAR 2017}{CS50's Introduction to Computer Science}{edx.org}{}{}{HarvardX - CS50 \newline  Harvard University's introduction to the intellectual enterprises of computer science and the art of programming. \newline Completed with \textbf{100/100} marks. \newline Certificate - \href{http://tiny.cc/amancs50}{tiny.cc/amancs50}}

%----------------------------------------------------------------------------------------
%	EXTRA CURRICULUM SECTION
%----------------------------------------------------------------------------------------

\section{Extra Curriculum Activities and Positions}

\cventry{2019}{}{}{}{}{ \textbf{Peer teaching} done for Object Oriented Programming for S.Y.B.tech students for a semester. 
}
\cventry{2019}{}{}{}{}{ Attended \textbf{Blockchain conference} organized by \textbf{TRAI} in Pune, India.
}
\cventry{2019}{}{}{}{}{ \textbf{3 times} Hacktoberfest contributor and won goodies. 
}
\cventry{2018}{}{}{}{}{ \textbf{Web manager} in GHRCEM's technical event \textbf{"Technowave"} and responsible for all the website related tasks.  
}
\cventry{2018}{}{}{}{}{ Won \textbf{debate competition} two times in a row with \textbf{1\textsuperscript{st} and 2\textsuperscript{nd} position} in college level competition.
}
\cventry{2017}{}{}{}{}{ Attended \textbf{"PYCON INDIA 2017"} in New Delhi, India.
}


%-----------------------------------------------------
%	PERSONAL DETAILS SECTION
%-----------------------------------------------------

\section{Personal Details}
\cventry{Language}{}{}{}{}{ English, Hindi, Bhojpuri }
\cventry{Hobbies}{}{}{}{}{ Speed cubing, Reading Books, Competitive programming, Open source contribution}


\end{document}